Luminance Constancy Learned from Labeled Naturalistic Images

### 2018-06-23 Draft5/draft5.tex
frustating edits

\title{Luminance Constancy Learned from Labeled Naturalistic Images}
%% Luminance constancy in naturalistic scenes
%% Learned luminance constancy: something
%%

\abstract{
The human visual system supports stable percepts of object color even though the light that reflects from object surfaces varies significantly with the scene illumination.
To understand the computations that support stable color perception, 
we study how estimating a target object's light reflectance value (LRV; a measure of the light reflected from the object under a standard illuminant) depends on variation in key properties of naturalistic scenes. 
Specifically, we study how variation in target object reflectance, illumination spectra, and the reflectance of background objects in a scene impact estimation of a target object's LRV. 
To do this, we applied supervised statistical learning methods to the simulated excitations of human cone photoreceptors, obtained from labeled naturalistic images.
The naturalistic images were rendered with computer graphics, with the underlying scene descriptions generated stochastically using statistical models
of natural spectral variation.
Optimally decoding target object LRV from the responses of a small learned set of task-specific linear filters that operate on a contrast representation of the cone excitations yields estimates that are within 13\% of the correct LRV.
% We show that a decoding scheme used learned linear filters to process a contrast representation of the cone excitations can recover target object LRV to within about 13\% RMSE.
% JDB: WE DIDN'T DEFINE RMSE SO IT MIGHT BE BEST TO AVOID USING THE ACRONYM HERE.
Our work provides a framework for evaluating how different sources of scene variability limit performance on luminance constancy.}

@@

 \author{Burge}{Johannes}
 {}
 {Department of Psychology, University of Pennsylvania, PA, USA}
 {}{jburge@psych.upenn.edu}

@@

Early work on computational color constancy considered a simplified imaging model where where scenes consisted of multiple flat matte objects and a single spatially diffuse illuminant \cite{LandRetinex,Buchsbaum80,MaloneyWandell86}.
Subsequent work incorporated probabilistic descriptions of the statistics of naturally occurring scenes \cite{D'ZmuraConstancy3, D'ZmuraIversonSinger,BrainardFreeman}.
A key insight from these computational studies is that stable color descriptors of a target object cannot be obtained solely from the light reflected from that target object.
It is possible, however, to obtain stable color descriptors by jointly analyzing the light reflected from multiple objects in the scene.
As a consequence, color constancy will be affected both by variation in the illumination and by variation in the surface reflectance of other objects in the scene.  Color constancy algorithms should therefore be evaluated with respect to variation in both of these factors \cite{BrainardWandellRetinex,BrainardFreeman}. 
There has also been computational work that generalizes to more complex viewing geometries \cite{funt1988color, barron2012color}.
% JDB: LAST SENTENCE DANGLES. HOW BOUT WE PUT IT LOWER DOWN IN THE MANUSCRIPT?

@@

% Figure 3
\begin{figure}
\centering
    \begin{subfigure}[b]{0.14 \textwidth}
        \caption{Big-ball}
        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure3/Figure3_a.png}
        \label{fig:libraryWithBigBall}
    \end{subfigure}
     ~ 
    \begin{subfigure}[b]{0.14 \textwidth}
        \caption{Xylophone}
        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure3/Figure3_b.png}
        \label{fig:libraryWithXylophone}
    \end{subfigure}
     ~ 
    \begin{subfigure}[b]{0.14 \textwidth}
        \caption{Barrel}
        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure3/Figure3_c.png}
        \label{fig:libraryWithBarrel}
         \end{subfigure}
    ~
	\begin{subfigure}[b]{0.14 \textwidth}
        \caption{Ring toy}
        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure3/Figure3_d.png}
        \label{fig:libraryWithRingToy}
    \end{subfigure}
        ~
    	\begin{subfigure}[b]{0.14 \textwidth}
        \caption{Bottle}
        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure3/Figure3_e.png}
        \label{fig:libraryWithChampagneBottle}
    \end{subfigure}
\caption{{\bf Library base scene with inserted objects.} The rendering package can be used to insert objects into base scenes. Each image shows a different object inserted into the Library base scene. The rendering viewpoint was set so that the object was at the center of the images. The full rendered images have been croppedso that the inserted objects are easily visible.}\label{fig:libraryWithTarget}
\end{figure}

The RenderToolbox4 package includes a collection of base scenes (Fig.~\ref{fig:baseScenes}).
% JDB: THE ABOVE SENTENCE IS CORRECT?
Base scenes specify an arrangement of objects and light sources.
Base scenes may be enriched by the insertion of additional objects, chosen from an object library (Fig.~\ref{fig:libraryWithTarget}), and by the insertion of additional light sources.
Once the position, size, and pose of the inserted objects and light sources have been set, 
a surface reflectance function can be assigned to each object in the scene, and a spectral power distribution function can be assigned to each light source (Fig.~\ref{fig:VWCCTransformations}). The resulting scene model can then be rendered from any specified viewpoint.

@@

The multivariate Gaussian model described above is based on normalized spectra. 
Thus, it does not embody the large variation in overall intensity of natural daylights.
To restore the overall intensity variation in the Granada dataset, which spans approximately three orders of magnitude, we scaled each randomly generated spectrum with a random number sampled from a log-uniform distribution spanning three orders of magnitude.
% JDB: THE NUMBERS [0.15, 150] ARE ARBITRARY. THE RELEVANT INFO IS THE NEXT SENTENCE.
% To restore the overall intensity variation in the Granada dataset, we scaled each randomly generated spectrum with a random number sampled from a log-uniform distribution in the range [0.15, 150].
% This procedure restores the three-order of magnitude intensity variation present in the original dataset.
The particular range of scale factors was chosen so that the mean number of cone isomerizations from the target object ranged from approximately 100 to 100,000, given a 100 ms cone integration time (see below).
This range of cone isomerizations corresponds approximately to that of natural daylight viewing.

@@

To put the computed cone excitations into a form for further analysis, we demosaiced the excitations for each cone class using linear interpolation
to obtain a cone excitation image for each cone class.
The lens and macular pigment absorb more short than long wavelength light, so that the excitations of the S cones tend to be
smaller than those of the L and M cones.
To make the magnitude of the three cone excitation images similar across cone classes, we
normalized each cone excitation image by the summed (over wavelength) quantal efficiency of the corresponding cone class.
The demosaicing and normalization do not alter the available information relative to that carried by the cone excitations themselves. 
% JDB: SHOULD WE SWAP 'SIGNAL TO NOISE' FOR 'AVAILABLE INFORMATION'.

@@

\subsubsection*{Learning optimal filters}
AMA is a task-specific Bayesian method for dimensionality reduction.
When provided with a labeled training set, a receptive field response model, a decoder that uses these responses to estimate the stimulus label, and a cost function, AMA returns a set of N linear receptive fields, where N is a parameter of the procedure.
These receptive fields are chosen so that decoding their responses leads to minimum expected-cost estimation, relative to any other choice of N linear receptive fields.
This is possible because given a training set together with a set of N linear receptive fields and an explicit cost function, it is possible to determine the minimum expected-cost estimator that maps receptive field responses to the stimulus labels.
% , on the assumption that all images in the training set are equally likely.
% JDB: CLAUSE SEEMS UNNECESSARY
Moreover, a close approximation to the corresponding expected estimation cost may be explicitly computed.
Thus, AMA searches over the space of linear receptive fields to find the set that minimizes the expected estimation cost.
For each condition, we learned the filters with a training set consisting of 90\% of the images.

@@

\subsubsection*{Baseline methods}
To provide baselines for evaluation of the estimation method described above, we used linear regression.
First, we solved for the weights on the average L, M and S cone excitations corresponding to the target object that best predicted the target LRV values.
We took the average cone responses from a $3 \times 3$ pixel region at the center of the target object.
This baseline method disregards information carried by the image regions corresponding to the background objects.
We also performed regression on the contrast normalized version of the cone excitation images.
This second baseline method indirectly incorporates information carried in the image regions corresponding to the background objects,
through their effect on the contrast normalized responses at the center of the target object. 
We also evaluated the performance of a naive model that uses the mean LRV value in the training set as the estimate, irrespective
of the image data; that is, the naive model always estimated the LRV to be equal to 0.4.
% JDB: DOUBLE CHECK THAT THE ADDITIONIAL CLAUSE AT END OF LAST SENTENCE IS CORRECT.

\section{Results} \label{Results}
%% Figure 10: Results for Condition 1
\begin{figure}
\centering
            \begin{subfigure}[b]{0.25 \textwidth}
        \caption{LRV estimates}
        \includegraphics[width=\textwidth, trim={0 0 0 1.3cm},clip]{../FiguresDraft5/Figure10/Figure10_a.pdf}
        \label{fig:case1Estimates}
    \end{subfigure} 
        \begin{subfigure}[b]{0.26 \textwidth}
        \caption{RF responses}
        \includegraphics[width=\textwidth, trim={0 3mm 0 15mm},clip]{../FiguresDraft5/Figure10/Figure10_b.pdf}
        \label{fig:case1RFResponse}
    \end{subfigure}
    \begin{subfigure}[b]{0.4 \textwidth}
	\caption{AMA receptive fields}
	\includegraphics[width=1.0\textwidth, trim={0.2cm -0.cm 0 0.3cm}]{../FiguresDraft5/Figure10/Figure10_c.pdf}
	\label{fig:case1RFs}
    \end{subfigure}   
    \caption{{\bf Condition 1 results:} (a) Mean estimated LRV $\pm$ 1 standard deviation for images in the test set obtained using the AMA-based estimator and linear regression on the cone excitations. Solid lines show the mean estimate, the filled region in lighter color shows $\pm$ 1 standard deviation. The diagonal identity line (dotted blue) indicates veridical estimation. The standard deviations are too small to be visible. Relative RMSE (see Fig.\ref{fig:barGraphs}) is 0.7\% for linear regression and 1.1\%  for AMA-based estimation. (b) Training image cone excitations in Condition 1 projected onto the first two AMA receptive fields. Each cluster of responses represents the image patches associated with a particular LRV. The response clusters are approximated by a multivariate Gaussians whose means and covariances are represented by the ellipses shown in the figure. (c) The first two AMA receptive fields.}
\label{fig:Condition1}
\end{figure}
%% DHB: "Linear Model" in panel a) should be "Regression".  Also in Figures 11 and 12.
%% DHB: It is really hard to see the ellipses in b), even if I increase the mag in the PDF.  Can you make them more salient?
%% DHB: Show first three RFs in (c) here and in Figure 12, I think.  Otherwise it is hard to understand why the ones in 12 change.
%% JDB: VIJAY, If you recompute the reduction in AMA cost for RFs 1, 2, and 3 in order and then compute the reduction in AMA cost for RFs 1, 3, and 2 in order, which of the two orders gives lower cost with two filters?

@@

The results in Figure~\ref{fig:Condition1} were obtained for one particular draw from our statistical model of illumination.
We verified that performance remained excellent for other draws.
%% VS to try a few more cases to make sure.

@@

%% Figure 12: Results for Condition 3
\begin{figure}
\centering
            \begin{subfigure}[b]{0.25 \textwidth}
        \caption{LRV estimates}
        \includegraphics[width=\textwidth, trim={0 0 0 1.3cm},clip]{../FiguresDraft5/Figure12/Figure12_a.pdf}
        \label{fig:case3Estimates}
    \end{subfigure} 
        \begin{subfigure}[b]{0.26\textwidth}
        \caption{Receptive field response}
        \includegraphics[width=\textwidth, trim={0 3mm 0 15mm},clip]{../FiguresDraft5/Figure12/Figure12_b.pdf}
        \label{fig:case3RFResponse}
    \end{subfigure}
    \begin{subfigure}[b]{0.4 \textwidth}
	\caption{AMA receptive fields}
	\includegraphics[width=1.0\textwidth, trim={0.2cm -0.cm 0 0.3cm}]{../FiguresDraft5/Figure12/Figure12_c.pdf}
	\label{fig:case3RFs}
    \end{subfigure}
    \caption{{\bf Condition 3 results:} (a) Mean estimated LRV $\pm$ 1 standard deviation for images in the test set obtained using the AMA-based estimator and linear regression from the contrast normalized cone excitations. The relative RMSE is 24.0\%  for linear regression and 13.1\% for AMA. (b) Contrast normalized cone excitations for the training set projected onto the first two AMA receptive fields. (c) First two AMA receptive fields learned using the contrast normalized cone excitations.}
\label{fig:Condition3}
\end{figure}

@@

Figure~\ref{fig:case3RFs} shows the first two receptive fields learned for Condition 3.
Similar to the receptive fields for Condition 1, the L and M cone excitations receive large weights, while the S cone excitations are less heavily weighted. 
Additionally, the cone excitations at the target have opposite sign compared to background object locations.
This make sense.
As discussed earlier, luminance is primarily determined by L and M cones, so the S cones should make little
contribution.
Additionally, for this condition, the optimal receptive fields compare normalized cone contrast between the target and background regions. 
This comparison may serve to reduce the effect of light scattered from the background onto the target. 
The specific geometry of the receptive fields should not be taken to be a general feature of the human visual system, as the RF geometry arises as a consequence of the fixed scene geometry used in the training set.
%% DHB: Let's look at RFs in case where secondary reflections are turned off, to see if what I drafted in this paragraph
% about RF structure is plausible.

@@

Figure~\ref{fig:barGraphs} summarizes our main findings, by showing the overall relative root mean squared estimation error (relative RMSE) for each condition. 
In Condition 1, where only the relative reflectance spectrum of the target object varies, 
luminance constancy is an easy computational problem,
and performance is essentially perfect for both the baseline linear regression and AMA methods.
In Condition 2, where the spectral power distribution of the illumination also varies, the problem of luminance constancy is more difficult.
Indeed, neither of our methods perform well when they operate directly on the cone excitations.
Performance with both methods improves greatly when the cone excitations are contrast normalized. 
Indeed, AMA performance for Condition 2 is essentially perfect, as it is in Condition 1.
Linear regression does less well, in part because it only has access to cone excitations at image locations
corresponding to the target object.
Condition 2, however, does not include scene-to-scene variation in the background surface reflectances,
as occurs in natural viewing.
The results for Condition 3 show performance when we add such variation.
Performance here represents the overall level of luminance constancy that our methods achieve for the
most realistic condition that we tested.
In this case, AMA-based estimates of target object LRV are, on average, within 13\% (relative RMSE) of the true value.
Introducing variation in the surface reflectance spectra of the background objects makes 
the luminance constancy problem substantially more difficult. 
Variation in the reflectance spectra of the background objects surfaces reduces how 
reliably light reflected from those objects can be used as a cue to estimate the spectral power distribution of the illuminant.
% JDB: Are we going to add in a constancy index, as we discussed doing a few meetings ago?
% DHB: I think it is time to submit this paper.

\subsection{Images of Virtual vs. Real Scenes}
As noted in the introduction, supervised learning requires large labeled datasets. Labeled datasets of natural images have been useful for developing normative models of the estimation of defocus blur, binocular disparity, retinal image motion, and 3D surface orientation \cite{burge2011optimal, burge2012optimal, burge2014optimal, burge2015optimal, kim2018lawful, burge2010natural, girshick2011cardinal, burge2016estimating, goncalves2017not}.

>>>>

\title{Luminance Constancy Learned from Labeled Naturalistic Images}

\abstract{
The human visual system supports stable percepts of object color even though the light that reflects from object surfaces varies significantly with the scene illumination.
To understand the computations that support stable color perception, 
we study how estimating a target object's light reflectance value (LRV; a measure of the light reflected from the object under a standard illuminant) depends on variation in key properties of naturalistic scenes. 
Specifically, we study how variation in target object reflectance, illumination spectra, and the reflectance of background objects in a scene impact estimation of a target object's LRV. 
To do this, we applied supervised statistical learning methods to the simulated excitations of human cone photoreceptors, obtained from labeled naturalistic images.
The naturalistic images were rendered with computer graphics, with the underlying scene descriptions generated stochastically using statistical models
of natural spectral variation.
Optimally decoding target object LRV from the responses of a small learned set of task-specific linear filters that operate on a contrast representation of the cone excitations yields estimates that are within 13\% of the correct LRV.
Our work provides a framework for evaluating how different sources of scene variability limit performance on luminance constancy.}

@@

 \author{Burge}{Johannes}
 {Neuroscience Graduate Group}
 {Department of Psychology, University of Pennsylvania, PA, USA}
 {}{jburge@psych.upenn.edu}

@@

Early work on computational color constancy considered a simplified imaging model where where scenes consisted of multiple flat matte objects and a single spatially diffuse illuminant \cite{LandRetinex,Buchsbaum80,MaloneyWandell86}.
Subsequent work incorporated probabilistic descriptions of the statistics of naturally occurring scenes \cite{D'ZmuraConstancy3, D'ZmuraIversonSinger,BrainardFreeman}.
A key insight from these computational studies is that stable color descriptors of a target object cannot be obtained solely from the light reflected from that target object.
It is possible, however, to obtain stable color descriptors by jointly analyzing the light reflected from multiple objects in the scene.
As a consequence, color constancy will be affected both by variation in the illumination and by variation in the surface reflectance of other objects in the scene.  Color constancy algorithms should therefore be evaluated with respect to variation in both of these factors \cite{BrainardWandellRetinex,BrainardFreeman}. 
There has also been computational work that generalizes to more complex viewing geometries \cite{funt1988color, barron2012color}.
% JDB: LAST SENTENCE DANGLES. HOW BOUT WE PUT IT LOWER DOWN IN THE MANUSCRIPT?
% Vijay: I agree

@@

% Figure 3
\begin{figure}
\centering
    \begin{subfigure}[b]{0.14 \textwidth}
        \caption{Big-ball}
        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure3/Figure3_a.png}
        \label{fig:libraryWithBigBall}
    \end{subfigure}
     ~ 
    \begin{subfigure}[b]{0.14 \textwidth}
        \caption{Xylophone}
        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure3/Figure3_b.png}
        \label{fig:libraryWithXylophone}
    \end{subfigure}
     ~ 
    \begin{subfigure}[b]{0.14 \textwidth}
        \caption{Barrel}
        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure3/Figure3_c.png}
        \label{fig:libraryWithBarrel}
         \end{subfigure}
    ~
	\begin{subfigure}[b]{0.14 \textwidth}
        \caption{Ring toy}
        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure3/Figure3_d.png}
        \label{fig:libraryWithRingToy}
    \end{subfigure}
        ~
    	\begin{subfigure}[b]{0.14 \textwidth}
        \caption{Bottle}
        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure3/Figure3_e.png}
        \label{fig:libraryWithChampagneBottle}
    \end{subfigure}
\caption{{\bf Library base scene with inserted objects.} The rendering package can be used to insert objects into base scenes. Each image shows a different object inserted into the Library base scene. The rendering viewpoint was set so that the object was at the center of the images. The full rendered images have been cropped so that the inserted objects are easily visible.}\label{fig:libraryWithTarget}
\end{figure}

The RenderToolbox4 package includes a collection of base scenes (Fig.~\ref{fig:baseScenes}).
Base scenes specify an arrangement of objects and light sources.
Base scenes may be enriched by the insertion of additional objects, chosen from an object library (Fig.~\ref{fig:libraryWithTarget}), and by the insertion of additional light sources.
Once the position, size, and pose of the inserted objects and light sources have been set, 
a surface reflectance function can be assigned to each object in the scene, and a spectral power distribution function can be assigned to each light source (Fig.~\ref{fig:VWCCTransformations}). The resulting scene model can then be rendered from any specified viewpoint.

@@

The multivariate Gaussian model described above is based on normalized spectra. 
Thus, it does not embody the large variation in overall intensity of natural daylights.
To restore the overall intensity variation in the Granada dataset, which spans approximately three orders of magnitude, we scaled each randomly generated spectrum with a random number sampled from a log-uniform distribution spanning three orders of magnitude.
% JDB: THE NUMBERS [0.15, 150] ARE ARBITRARY. THE RELEVANT INFO IS THE NEXT SENTENCE.
% To restore the overall intensity variation in the Granada dataset, we scaled each randomly generated spectrum with a random number sampled from a log-uniform distribution in the range [0.15, 150].
% This procedure restores the three-order of magnitude intensity variation present in the original dataset.
% Vijay: This would needed by someone who wants to reproduce the results.
The particular range of scale factors was chosen so that the mean number of cone isomerizations from the target object ranged from approximately 100 to 100,000, given a 100 ms cone integration time (see below).
This range of cone isomerizations corresponds approximately to that of natural daylight viewing.

@@

To put the computed cone excitations into a form for further analysis, we demosaiced the excitations for each cone class using linear interpolation
to obtain a cone excitation image for each cone class.
The lens and macular pigment absorb more short than long wavelength light, so that the excitations of the S cones tend to be
smaller than those of the L and M cones.
To make the magnitude of the three cone excitation images similar across cone classes, we
normalized each cone excitation image by the summed (over wavelength) quantal efficiency of the corresponding cone class.
The demosaicing and normalization do not alter the available information relative to that carried by the cone excitations themselves. 
% JDB: SHOULD WE SWAP 'SIGNAL TO NOISE' FOR 'AVAILABLE INFORMATION'.
% Vijay: No.

@@

\subsubsection*{Learning optimal filters}
AMA is a task-specific Bayesian method for dimensionality reduction.
When provided with a labeled training set, a receptive field response model, a decoder that uses these responses to estimate the stimulus label, and a cost function, AMA returns a set of N linear receptive fields, where N is a parameter of the procedure.
These receptive fields are chosen so that decoding their responses leads to minimum expected-cost estimation, relative to any other choice of N linear receptive fields.
This is possible because given a training set together with a set of N linear receptive fields and an explicit cost function, it is possible to determine the minimum expected-cost estimator that maps receptive field responses to the stimulus labels.
Moreover, a close approximation to the corresponding expected estimation cost may be explicitly computed.
Thus, AMA searches over the space of linear receptive fields to find the set that minimizes the expected estimation cost.
For each condition, we learned the filters with a training set consisting of 90\% of the images.

@@

\subsubsection*{Baseline methods}
To provide baselines for evaluation of the estimation method described above, we used linear regression.
First, we solved for the weights on the average L, M and S cone excitations corresponding to the target object that best predicted the target LRV values.
We took the average cone responses from a $3 \times 3$ pixel region at the center of the target object.
This baseline method disregards information carried by the image regions corresponding to the background objects.
We also performed regression on the contrast normalized version of the cone excitation images.
This second baseline method indirectly incorporates information carried in the image regions corresponding to the background objects,
through their effect on the contrast normalized responses at the center of the target object. 
We also evaluated the performance of a naive model that uses the mean LRV value in the training set as the estimate, irrespective
of the image data; that is, the naive model always estimated the LRV to be equal to 0.4.

\section{Results} \label{Results}
%% Figure 10: Results for Condition 1
\begin{figure}
\centering
            \begin{subfigure}[b]{0.3 \textwidth}
        \caption{LRV estimates}
        \includegraphics[width=\textwidth, trim={0 0 0 1.3cm},clip]{../FiguresDraft5/Figure10/Figure10_a.pdf}
        \label{fig:case1Estimates}
    \end{subfigure} 
        \begin{subfigure}[b]{0.31 \textwidth}
        \caption{RF responses}
        \includegraphics[width=\textwidth, trim={0 3mm 0 15mm},clip]{../FiguresDraft5/Figure10/Figure10_b.pdf}
        \label{fig:case1RFResponse}
    \end{subfigure}
    \begin{subfigure}[b]{0.32 \textwidth}
	\caption{AMA receptive fields}
	\includegraphics[width=1.0\textwidth, trim={0.2cm -0.cm 0 0.3cm}]{../FiguresDraft5/Figure10/Figure10_c.pdf}
	\label{fig:case1RFs}
    \end{subfigure}   
    \caption{{\bf Condition 1 results:} (a) Mean estimated LRV $\pm$ 1 standard deviation for images in the test set obtained using the AMA-based estimator and linear regression on the cone excitations. Solid lines show the mean estimate, the filled region in lighter color shows $\pm$ 1 standard deviation. The diagonal identity line (dotted blue) indicates veridical estimation. The standard deviations are too small to be visible. Relative RMSE (see Fig.\ref{fig:barGraphs}) is 0.7\% for linear regression and 1.1\%  for AMA-based estimation. (b) Training image cone excitations in Condition 1 projected onto the first two AMA receptive fields. Each cluster of responses represents the image patches associated with a particular LRV. The response clusters are approximated by a multivariate Gaussians whose means and covariances are represented by the ellipses shown in the figure. (c) The first two AMA receptive fields.}
\label{fig:Condition1}
\end{figure}
%% JDB: VIJAY, If you recompute the reduction in AMA cost for RFs 1, 2, and 3 in order and then compute the reduction in AMA cost for RFs 1, 3, and 2 in order, which of the two orders gives lower cost with two filters? 
% Vijay: See my email.

@@

The results in Figure~\ref{fig:Condition1} were obtained for one particular draw from our statistical model of illumination.
We verified that performance remained excellent for other draws.
%% VS to try a few more cases to make sure.
% Vijay: Tried. Results are similar.

@@

%% Figure 12: Results for Condition 3
\begin{figure}
\centering
            \begin{subfigure}[b]{0.3 \textwidth}
        \caption{LRV estimates}
        \includegraphics[width=\textwidth, trim={0 0 0 1.3cm},clip]{../FiguresDraft5/Figure12/Figure12_a.pdf}
        \label{fig:case3Estimates}
    \end{subfigure} 
        \begin{subfigure}[b]{0.31\textwidth}
        \caption{Receptive field response}
        \includegraphics[width=\textwidth, trim={0 3mm 0 15mm},clip]{../FiguresDraft5/Figure12/Figure12_b.pdf}
        \label{fig:case3RFResponse}
    \end{subfigure}
    \begin{subfigure}[b]{0.32 \textwidth}
	\caption{AMA receptive fields}
	\includegraphics[width=1.0\textwidth, trim={0.2cm -0.cm 0 0.3cm}]{../FiguresDraft5/Figure12/Figure12_c.pdf}
	\label{fig:case3RFs}
    \end{subfigure}
    \caption{{\bf Condition 3 results:} (a) Mean estimated LRV $\pm$ 1 standard deviation for images in the test set obtained using the AMA-based estimator and linear regression from the contrast normalized cone excitations. The relative RMSE is 24.0\%  for linear regression and 13.1\% for AMA. (b) Contrast normalized cone excitations for the training set projected onto the first two AMA receptive fields. (c) First two AMA receptive fields learned using the contrast normalized cone excitations.}
\label{fig:Condition3}
\end{figure}

@@

Figure~\ref{fig:case3RFs} shows the first two receptive fields learned for Condition 3.
Similar to the receptive fields for Condition 1, the L and M cone excitations receive large weights, while the S cone excitations are less heavily weighted. 
Additionally, the cone excitations at the target have opposite sign compared to background object locations.
This make sense.
As discussed earlier, luminance is primarily determined by L and M cones, so the S cones should make little
contribution.
Additionally, for this condition, the optimal receptive fields compare normalized cone contrast between the target and background regions. 
This comparison may serve to reduce the effect of light scattered from the background onto the target. 
The specific geometry of the receptive fields should not be taken to be a general feature of the human visual system, as the RF geometry arises as a consequence of the fixed scene geometry used in the training set.

@@

Figure~\ref{fig:barGraphs} summarizes our main findings, by showing the overall relative root mean squared estimation error (relative RMSE) for each condition. 
In Condition 1, where only the relative reflectance spectrum of the target object varies, 
luminance constancy is an easy computational problem,
and performance is essentially perfect for both the baseline linear regression and AMA methods.
In Condition 2, where the spectral power distribution of the illumination also varies, the problem of luminance constancy is more difficult.
Indeed, neither of our methods perform well when they operate directly on the cone excitations.
Performance with both methods improves greatly when the cone excitations are contrast normalized. 
Indeed, AMA performance for Condition 2 is essentially perfect, as it is in Condition 1.
Linear regression does less well, in part because it only has access to cone excitations at image locations
corresponding to the target object.
Condition 2, however, does not include scene-to-scene variation in the background surface reflectances,
as occurs in natural viewing.
The results for Condition 3 show performance when we add such variation.
Performance here represents the overall level of luminance constancy that our methods achieve for the
most realistic condition that we tested.
In this case, AMA-based estimates of target object LRV are, on average, within 13\% (relative RMSE) of the true value.
Introducing variation in the surface reflectance spectra of the background objects makes 
the luminance constancy problem substantially more difficult. 
Variation in the reflectance spectra of the background objects surfaces reduces how 
reliably light reflected from those objects can be used as a cue to estimate the spectral power distribution of the illuminant.

\subsection{Images of Virtual vs. Real Scenes}
As noted in the introduction, supervised learning requires large labeled datasets. Labeled datasets of natural images have been useful for developing normative models of the estimation of defocus blur, binocular disparity, retinal image motion, and 3D surface orientation \cite{burge2011optimal, burge2012optimal, burge2014optimal, burge2015optimal, sebastian2015defocus, kim2018lawful, burge2010natural, girshick2011cardinal, burge2016estimating, goncalves2017not}.
